GMSE: an R package for generalised management strategy evaluation

### 2017-10-18 notebook/ms/ms.Rmd
Minor edits to Introduction

Many global natural resources, including the biodiversity on which critical ecosystem services depend, are in a state of severe decline [@Dirzo2014; @Hautier2015; @Ceballos2017; @OConnell2017]. Conservation of biodiversity can be complicated by the immediate need to use natural resources and land area for human livelihood (e.g., food production), causing real or perceived conflicts between conservation and food security and creating a challenge for the management of many natural resources [@Redpath2015a]. Given an increasing human population [@Crist2017], the number and intensity of such conflicts are likely to increase into the twenty first century. Effective management tools are therefore needed for the long-term sustainable use of natural resources under the rising demand for food production [@Fischer2017].

@@

The GMSE R package is a flexible, highly mechanistic, agent-based modelling tool to simulate all key aspects of natural resource management. GMSE considers a range of parameters to simulate resource dynamics and management policy options, and uses genetic algorithms to dynamically model stakeholder (manager and user) decision-making. Genetic algorithms find adaptive solutions to any simulated conditions given stakeholder-specific goals, allowing GMSE to model scenarios of conservation conflict.

>>>>

Many global natural resources, including the biodiversity on which critical ecosystem services depend, are in a state of severe decline [@Dirzo2014; @Hautier2015; @Ceballos2017; @OConnell2017]. Conservation of biodiversity can be complicated by the immediate need to use natural resources and land area for human livelihood (e.g., food production), causing real or perceived conflicts between conservation and food security and creating a challenge for the management of many natural resources [@Redpath2015a]. Given increasing human population size [@Crist2017], the number and intensity of such conflicts are likely to increase into the twenty first century. Effective management tools are therefore needed for the long-term sustainable use of natural resources under the rising demand for food production [@Fischer2017].

@@

The R package 'GMSE' is a flexible modelling tool to simulate all key aspects of natural resource management. GMSE offers a range of parameters to simulate resource dynamics and management policy options, and includes genetic algorithms to dynamically model stakeholder (manager and user) decision-making. Genetic algorithms find adaptive solutions to any simulated conditions given stakeholder-specific goals, allowing GMSE to model scenarios of conservation conflict.
